Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2018-06-14 inst/examples/20170201-manuscript.Rmd

  df2 <- subset(df00, catalog == catal) %>%
           group_by(publication_decade, gatherings) %>%
	   summarize(paper = sum(paper, na.rm = TRUE), n = n())

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

@@

  p <- p + 
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10) #+

>>>>

  df2 <- subset(df00, catalog == catal) %>%
           group_by(publication_decade, gatherings) %>%
	   summarize(paper = sum(paper, na.rm = TRUE)/1e6, n = n())
  # Million sheets

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (million sheets)")
  # p <- p + ylim(c(0, max(na.omit(df00$paper))))

@@

  p <- p + 
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, 6.8, 1), limits = c(0, 6.8))
         #scale_y_continuous(breaks = seq(0, max(df00$paper, na.rm = TRUE), 1000))
	                    # label = scientific_10)
